Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-05-01 SupportingInformation.Rmd

<!--adding plots showing results to confirm hypothesis behind third mechanism-->
\begin{figure}[!h]
\textbf{ \hspace{6.5 cm} (A) \hspace{2 cm} (B) \hspace{2 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/ExtremeL_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (D) \hspace{2 cm} (E) \hspace{2 cm} (F)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/SomewhatL_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (G) \hspace{2 cm} (H) \hspace{2 cm} (I)} \\
\vspace{-0.7 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/BivNormal_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (J) \hspace{2 cm} (K) \hspace{2 cm} (L)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/SomewhatR_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (M) \hspace{2 cm} (N) \hspace{2 cm} (O)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/ExtremeR_hist_taildep.pdf}\\
\caption[Non-parametric statistics on a mechanism of tail dependence in character distributions]{Three 
measures of asymmetry of tail dependence between two characters, across extant species ($\cor_{0,0.2}-\cor_{0.8,1}$ (A, D, G, J, M), 
$\Ps_{0,0.2}-\Ps_{0.8,1}$ (B, E, H, K, N), and $\Dsq_{0.8,1}-\Dsq_{0,0.2}$ (C, F, I, L, O)) were 
computed for each of 100 simulations for each of five types of tail dependence between 
evolutionary changes in the characters (extreme left-tail dependence (A-C), moderate left-tail dependence (D-F), 
symmetry of tail dependence (G-I), moderate right-tail dependence (J-L), and extreme right-tail dependence 
(M-O)). Asymmetry of tail dependence in evolutionary changes in characters tended to beget similar
asymmetry in the characters across extant species. For additional details see 
Appendix \ref{evol_mech}.\label{fig_cop_evo}}
\end{center}
\end{figure}

>>>>

<!--adding plots showing results to confirm hypothesis behind third mechanism-->
\begin{figure}[!h]
\textbf{ \hspace{6.5 cm} (A) \hspace{2 cm} (B) \hspace{2 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/ExtremeL_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (D) \hspace{2 cm} (E) \hspace{2 cm} (F)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/SomewhatL_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (G) \hspace{2 cm} (H) \hspace{2 cm} (I)} \\
\vspace{-0.7 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/BivNormal_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (J) \hspace{2 cm} (K) \hspace{2 cm} (L)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/SomewhatR_hist_taildep.pdf}\\
\end{center}
\textbf{ \hspace{6.5 cm} (M) \hspace{2 cm} (N) \hspace{2 cm} (O)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=9 cm]{./Results/BMR_results/evo_cop/ExtremeR_hist_taildep.pdf}\\
\caption[Non-parametric statistics on a mechanism of tail dependence in character distributions]{Three 
measures of asymmetry of tail dependence ($\cor_{0,0.2}-\cor_{0.8,1}$ (A, D, G, J, M), 
$\Ps_{0,0.2}-\Ps_{0.8,1}$ (B, E, H, K, N), and $\Dsq_{0.8,1}-\Dsq_{0,0.2}$ (C, F, I, L, O)) between two characters, across extant species,  were 
computed for each of 100 simulations of mammalian evolution for each of five types of tail dependence between 
evolutionary changes in the characters (extreme left-tail dependence (A-C), moderate left-tail dependence (D-F), 
symmetry of tail dependence (G-I), moderate right-tail dependence (J-L), and extreme right-tail dependence 
(M-O)). Asymmetry of tail dependence in evolutionary changes in characters tended to beget similar
asymmetry in the characters across extant species. For additional details see 
Appendix \ref{evol_mech}. The number in the upper right of each panel indicates how many statistics out of $100$ were less than or equal to $0$. Values substantially lower (respectively, higher) than $50$ therefore indicate greater left (respectively, right) tail-dependence between characters.\label{fig_cop_evo}}
\end{center}
\end{figure}
